Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
Added basic type definitions and addressed changes to function types.

\langName has a very simple type system, including only integers and lambda
abstractions, which include fixpoints by default, along with appropriate
security labels for both.  In \langName, security labels specify confidentiality
policies, specifying what other data the labelled data can affect.\footnote{It is
not difficult to imagine how to extend our system to include integrity labels.
However, for the sake of simplicity, we decided to concern ourselves with only
confidentiality at first}  Data can only be affected by items at the same label
or lower (so high data can not affect low labelled data).

\textbf{TODO: Give definition of types in the language and discuss stuff that
was dropped from \origLang}

>>>>

\langName has a very simple type system, including only integers and lambda
abstractions, which include fixpoints by default, along with appropriate
security labels for both, as shown in Figure~\ref{fig:types}.  In \langName,
security labels specify confidentiality policies, specifying what other data the
labelled data can affect.\footnote{It is not difficult to imagine how to extend
our system to include integrity labels.  However, for the sake of simplicity, we
decided to concern ourselves with only confidentiality at first}  Data can only
be affected by items at the same label or lower (so high data can not affect low
labelled data).

\begin{figure}[h!]
  \begin{align*}
    t ::= int^l \: | \: (t -> t)^l
  \end{align*}
  \caption{Types for \langName}
  \label{fig:types}
\end{figure}

A reader familiar with the type system for \origLang will notice that our type
system does not include types above the arrow in the function type, for giving
security bounds on side effects of the function, and the type does not include
effect labels for exceptions.  These are dropped as a result of the
simplifications we made in defining \langName, since there are no side effects
or exceptions in the language.
